\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2018-08-07 paper/ms.tex
Mention p vs. P

\section{Introduction}
Bayesian inference, where probability theory describes degrees of
logical implication or subjective certainty, provides a powerful general basis
for data analysis \citep{o2004kendall, sivia2006data}. The result of such
an analysis is typically
posterior probabilities of various hypotheses, or
a joint posterior probability distribution for the values of unknown
parameters.

In compact but standard notation, the posterior distribution for
parameters $\params$ given data $\data$, within the context of prior
information $M$, is
\begin{align*}
p(\params | \data, M) &=
\frac{p(\params | M)p(\data | \params, M)}{p(\data | M)}
\end{align*}
or
\begin{align*}
\textnormal{posterior} &=
\frac{\textnormal{prior} \times \textnormal{likelihood}}
     {\textnormal{marginal likelihood}}.
\end{align*}

>>>>

\section{Introduction}
Bayesian inference, where probability theory describes degrees of
logical implication or subjective certainty, provides a powerful general basis
for data analysis \citep{o2004kendall, sivia2006data}. The result of such
an analysis is typically
posterior probabilities of various hypotheses, or
a joint posterior probability distribution for the values of unknown
parameters. Throughout this paper we denote probability distributions
using a lower case $p$ and probabilities with an upper case $P$.

In a standard Bayesian inference situation, the posterior distribution for
parameters $\params$ given data $\data$, within the context of prior
information $M$, is
\begin{align*}
p(\params | \data, M) &=
\frac{p(\params | M)p(\data | \params, M)}{p(\data | M)}
\end{align*}
or
\begin{align*}
\textnormal{posterior} &=
\frac{\textnormal{prior} \times \textnormal{likelihood}}
     {\textnormal{marginal likelihood}}.
\end{align*}
